Assessing spatial correlations in pulsar timing arrays with the noise-marginalized optimal statistic

### 2017-08-04 manuscript/manuscript.tex
added citations

We used the same scrambled sky positions as were used in \citet{tlb+2017}. 
These positions were chosen so as to minimize the overlap  
between the scrambled ORFs and the true ORF, 
which can be assessed using the ``match statistic'' \citep{cs2016}:
\begin{equation}
	\bar{M} = \frac{\sum_{I,J \neq I} \Gamma_{IJ} \Gamma'_{IJ}}{\sqrt{ \left( \sum_{I, J \neq I} \Gamma_{IJ} \Gamma_{IJ} \right) \left( \sum_{I, J \neq I} \Gamma'_{IJ} \Gamma'_{IJ} \right)}} \,,
\end{equation}
where $I$,$J$ index the pulsar number, and $\Gamma$ and $\Gamma'$ are two different ORFs. 
The 210 sky scrambles used in this paper were generated using a particle swarm optimization (PSO) algorithm 
with the requirement that the scrambled ORFs had $\bar{M} < 0.1$ when compared to the true ORF and to each other.
\sv{Steve, check this section}

>>>>

We used the same scrambled sky positions as were used in \citet{tlb+2017}. 
These positions were chosen so as to minimize the overlap  
between the scrambled ORFs and the true ORF, 
which can be assessed using the ``match statistic'' \citep{cs2016}:
\begin{equation}
	\bar{M} = \frac{\sum_{I,J \neq I} \Gamma_{IJ} \Gamma'_{IJ}}{\sqrt{ \left( \sum_{I, J \neq I} \Gamma_{IJ} \Gamma_{IJ} \right) \left( \sum_{I, J \neq I} \Gamma'_{IJ} \Gamma'_{IJ} \right)}} \,,
\end{equation}
where $I$,$J$ index the pulsar number, and $\Gamma$ and $\Gamma'$ are two different ORFs. 
The 210 sky scrambles used in this paper were generated 
using a particle swarm optimization (PSO) algorithm \citep{ke1995,se1998} 
with the requirement that the scrambled ORFs had $\bar{M} < 0.1$ when compared to the true ORF and to each other.
\sv{Steve, check this section}
